---
title: "My R Markdown Primer"
author: "Angelica Wright"
date: "2026-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 
R Markdown lets users bring together the text, R code, and a document that can be duplicated into a document. To use R Markdown you you can write text and then Rstudio will use the knits function to link it all together into a HTML, PDF, or word doc

#Markdown  
This is the narrative paragraph that provides more context down which can help with the formattin and structure of my document. 

#LaTEX Math
Inline math: $\alpha + \beta = \gamma$

Displayed equation:
Displayed equation:

\[
a + b = c
\]

#Code Chunks

```{r}
cigs <- read.csv("CigarettesB.csv")
summary(cigs)
```

```{r}
library(ggplot2)

ggplot(cigs, aes(price, packs)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
`
#Reflection 
Using R Markdown was efficient in being able to communicate the necessary steps and made a lot more sense in trying to take notes while adding in real world application to the programming. 

